From the function-sheaf dictionary to quasicharacters of $p$-adic tori

### 2014-10-01 dictionary.tex
Connected! -- was needed in the first sentence of Intro!

Motivated by an application to the geometrization and categorification of quasicharacters of $p$-adic tori,
this paper extends Deligne's function-sheaf dictionary from commutative algebraic groups to smooth commutative group schemes over finite fields.

>>>>

Motivated by an application to the geometrization and categorification of quasicharacters of $p$-adic tori,
this paper extends Deligne's function-sheaf dictionary from connected commutative algebraic groups to smooth commutative group schemes over finite fields.
